\addcontentsline{toc}{chapter}{Bibliographie}
\begin{thebibliography}{}

\bibitem{BL00}
{\scshape Y. Bdolah et D. Livnat} -- Reinforcement learning playing tetris,  2000. Disponible à l'adresse \url{http://www.math.tau.ac.il/~mansour/rl-course/student_proj/livnat/tetris.html}

\bibitem{Bru92}
{\scshape J. Brzustowski} -- \textit{Can You Win at TETRIS?} T. N.p., 1992. Web. 21 Jan. 2019. Retrospective Theses and Dissertations, 1919-2007. Disponible à l'adresse \url{https://open.library.ubc.ca/collections/ubctheses/831/items/1.0079748}

\bibitem{}
{\scshape J. Greaves} -- Understanding RL: The Bellman Equations, Post de blog daté du 9 novembre 2017. Disponible à l'adresse \url{https://joshgreaves.com/reinforcement-learning/understanding-rl-the-bellman-equations/}

\bibitem{}
{\scshape S. Kistemaker} -- Cross-Entropy Method for Reinforcement Learning, Thesis for Bachelor Artificial Intelligence, 2008. Disponible à l'adresse \url{https://staff.fnwi.uva.nl/b.bredeweg/pdf/BSc/20072008/Kistemaker.pdf}

\bibitem{LB09}
{\scshape B.~{Loguidice} et M.~~{Barton}} -- \textit{{VINTAGE GAMES. An  Insider Look  at the History of Grand Theft Auto, Super Mario, and the Most Influential Games of All Time}}, Elsevier, Focal Press, Amsterdam, 2009, p.~291--301.

\bibitem{}
{\scshape D.~{Sheff}} -- \textit{{GAME OVER. Press Start to Continue}}, GamePress, CyberActive Publishing In., Wilton, 1999, p.~292--348.

\bibitem{}
{\scshape B. Scherrer, M. Ghavamzadeh, V. Gabillon, B. Lesner et M. Geist} -- Approximate Modified Policy Iteration and its Application to the Game of Tetris, \textit{Journal of Machine Learning Research} \textbf{16} (2015), pp. 1629-1676

\bibitem{}
{\scshape M. Stevens et S. Pradhan} -- Playing Tetris with Deep Reinforcement Learning. Report for Stanford course CS231n: Convolutional Neural Networks for Visual Recognition, 2016. Disponible à l'adresse \url{http://cs231n.stanford.edu/reports/2016/pdfs/121_Report.pdf}

\bibitem{}
{\scshape R. S. Sutton et A.G. Barto} -- \textit{{Reinforcement Learning: An introduction}}, 2nd ed., MIT Press, Cambridge, MA, 2018.

\end{thebibliography}